Dynamics of Laterally Propagating Flames in X-ray Bursts

### 2019-08-17 xrb/paper.tex
more work on the paper

@@

@@

>>>>

\begin{deluxetable}{lccccc}
\tablecaption{\label{table:sim_names} Simulaiton parameters.}
\tablehead{\colhead{name} & \colhead{reaction boost} & \colhead{conductivity boost} & \colhead{fine grid resolution} & \colhead{rotation rate}  & \colhead{network}}
\startdata
10/10 & 10 & 10 & 10~cm & 2000~Hz & {\tt aprox13} \\
10/10-slow & 10 & 10 & 10~cm & 1000~Hz & {\tt aprox13} \\
10/10-lores & 10 & 10 & 20~cm & 2000~Hz & {\tt aprox13} \\
5/5 & 5 & 5 & 10~cm & 2000~Hz & {\tt aprox13} \\
10/10-iso7 & 10 & 10 & 10~cm & 2000~Hz & {\tt iso7} \\
\enddata
\end{deluxetable}

@@

% made with time_series.py in flame_wave_boost_10_10_paper with --skip 100
\begin{figure}[h]
\centering
\plotone{time_series}
\caption{\label{fig:time_series} Time series of the mean molecular weight of the 
flame for our standard 10/10 simulation.}
\end{figure}

% made with overview.py
\begin{figure}[h]
\centering
\plotone{flame_boost_10_10_overview}
\caption{\label{fig:10_10_overview} Temperature, energy generation rate, and out-of-plane velocity for the 10/10 simulation.}
\end{figure}

@@

\begin{figure}[h]
\centering
\plotone{flame_wave_boost_5_5_slice}
\caption{\label{fig:5_5_overview} Temperature, mean molecular weight, energy generation rate, and out-of-plane velocity for the 5/5 simulation.}
\end{figure}
